\section{Complexity Class P}
\begin{itemize}
    \item (D)TIME[F]: class of algorithms that are $O(f)$
    \item $P=\bigcup\limits_{k\geq 0}\text{TIME}[n^k]$
    \item P problems are tractable in practise
\end{itemize}

\subsection{Satisfiability Problem}
Can a $k$-CNF problem be satisfied. 2-Sat is in P.

\subsection{Polynomial Reducability}
If $L_1 \leq L_2$ and $L_2\in P \Rightarrow L_1 \in P$\\
2-colourability $\leq$ 2-sat

\section{Complexity Class NP}
\subsection{Certificates}
\begin{itemize}
    \item Short and easily checkable
    \item Satisfiability: truth assignment
    \item K-Colourability: A proper colouring
\end{itemize}
Class of languages which have P verifiers are NP.

\subsubsection{Composite Number}
Are there integers such that $u\cdot v=k$

\subsubsection{Subset Sum}
Is there  a subset of integers which equals $k$.

\subsection{Non-determinism in NP}
Time complexity of a non-deterministic TM is the number of steps in the shortest accepting/rejecting path.\\
If not all paths halt, NT is undefined.\\
NTIME[f] is the class of all problems where an algorithm exists with non-deterministic time complexity $O(f)$.\\
$$NP=\bigcup\limits_{k\geq 0}\text{NTIME}[n^k]$$
NP means non-deterministic polynomial time.

\subsubsection{Complete Problems}
No problems in the class that are strictly harder

\subsubsection{NP-Complete}
Hardest problems in NP. Satisfiability is first NP-complete problem.

\subsubsection{NP-Intermediate}
If $P\neq NP$, there are infinitely many problems that are neither P/NP-complete. E.g.\ Graph Isomorphism.

\subsection{NP-Completeness}
Two ways for polynomial time reduction:
\begin{enumerate}
    \item $X\rightarrow Y$ in P steps
    \item Solve Y using P number of calls to an oracle
\end{enumerate}

Two ways to prove NP-Completeness:
\begin{enumerate}
    \item Show problem is in NP
    \item Find known NP-complete problem and show it is equivalent.
\end{enumerate}

NP-Hard if 2 is possible but not 1.

\subsubsection{Pseudo-Polynomial Time}
If length of input is not bounded by a polynomial function of the input length, e.g.\ knapsack.

\subsubsection{Strongly/Weakly NP-Complete}
Strongly if it remains NP-complete when numbers in input are bounded.\\
Usually problems not containing numerical data + TSP are strongly NP-Complete.\\
Subset sum and Partition are weakly NP-Complete.

\subsubsection{coNP}
For when $L$ and $\bar{L}$ have a P verifier. E.g.\ NO hamiltonian cycle and tautology.

\subsubsection{coNP-completeness}
If equivalent to another problem in coNP and both $L$ and $\bar{L}$ are NP-complete.
